##Fitness Analysis
author: Abhishek Sehgal


 
*Set Working directory*

```{r workdir}

setwd("C:\\Users\\abhishek\\coursera\\5 - reproducible research\\week 2")  
```

*Load the Activity.csv dataset*

```{r loaddata}
act<-read.csv("activity.csv",stringsAsFactors=FALSE)  
```

*- Getting Total Steps in a day*
*1. Plotting graph*
*2. Mean daily steps*
*3. Median daily steps*

```{r totsteps}
library(data.table)
acttot<-data.table(act)[,sum(steps,na.rm=TRUE),by=date]
setnames(acttot,names(acttot),c("date","tsum"))
acttot$date<-sapply(acttot[,date],as.Date,format="%Y-%m-%d")

par(mar=c(4,4,4,4))
plot(acttot$date,acttot$tsum,type="h",lwd=4,xlab="Date",ylab="Steps")

mean(acttot$tsum)

median(acttot$tsum)
```
*- Getting mean Steps in 5min interval*
*1. Mean step by interval*
*2. Plotting graph*
*3. Max steps interval*

```{r meansteps}

actm<-data.table(act)[,mean(steps,na.rm=TRUE),by=interval]

plot(x=actm$interval,y=actm$V1,xlab="interval",ylab="steps",type="l")

actm[,interval][which.max(actm$V1)]
```


*Imputing values*
*1. Total no of missing values*
*2  Imputing missing values*
*3. plot new total graph*
*4. new mean and median*
```{r imputevalues}


a<-is.na(act)
sum(a)

acti<-data.table(act)
acti[is.na(acti$steps),1]<-mean(acti[,steps],na.rm=TRUE)

at<-acti[,sum(steps,na.rm=TRUE),by=date]
setnames(at,names(at),c("date","tsum"))
at$date<-sapply(at[,date],as.Date,format="%Y-%m-%d")

par(mar=c(4,4,4,4))
plot(at$date,at$tsum,type="h",lwd=4,xlab="Date",ylab="Steps")

mean(at$tsum)

median(at$tsum)
```

